Welcome Home --- Now Vote!

### 2020-07-06 markdown/part2/blind.tex
commit july 6

\title{Welcome Home --- Now Vote!\thanks{Prepared for the 2020 Annual Meeting of the Midwest Political Science Association. The author thanks Jacob Faber, Jeff Manza, Myrna Pérez, Ariel White, and Peter Miller for their comments on this project. All errors are my responsibility.}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Voting Rights Restoration and Post-Supervision Participation}
\author{Kevin Morris\footnote{Researcher, Brennan Center for Justice at NYU School of Law, 120 Broadway Ste 1750, New York, NY 10271 (\href{mailto:kevin.morris@nyu.edu}{\nolinkurl{kevin.morris@nyu.edu}})}}
\date{March 09, 2020
\linebreak
\linebreak
\linebreak
\linebreak
Word Count: 9,596}

@@

In all but two states (Maine and Vermont), felony disenfranchisement laws mean that American citizens convicted of felony offenses lose the right to vote for at least some period of time. In some states, such as Oregon and Massachusetts, individuals lose that right only for the period in which they are actively incarcerated. Iowa stands alone at the other end of the spectrum, where felony convictions result in lifelong disenfranchisement unless a returned citizen receives an individual pardon from the state's governor (Justice \protect\hyperlink{ref-bcj_laws}{2019}). This variation in laws arises from language in the Fourteenth Amendment which allows states to revoke individuals' voting rights ``for participation in rebellion, or other crime.'' The definition of ``other crime,'' left so vague in the Constitution, is now generally used by states to disenfranchise citizens for any felony offense. The Supreme Court, in cases such as \emph{Richardson v. Ramirez} (1974), has upheld this practice. Collectively, these laws disenfranchise as many as 4.7 million American citizens. Of these, the majority are no longer incarcerated (Uggen, Larson, and Shannon \protect\hyperlink{ref-sentencing_2016}{2016}).\footnote{The figures reported in Uggen, Larson, and Shannon (\protect\hyperlink{ref-sentencing_2016}{2016}) have been adjusted to reflect the impact of Amendment 4 in Florida.}

@@

Following Executive Order 181, the Department of Corrections and Community Supervision began indicating on their online Parolee Lookup Tool whether a parolee had her voting rights restored. By using the identification number provided from the parolee public records request and this website, I was able to identify individuals who had their voting rights restored.\footnote{Not all parolees listed in the public records request data are included in the lookup tool. Roughly 1 percent of former parolees are not in the online lookup.} There were 3,093 individuals who were discharged from parole before the registration deadline whose rights were restored while still under supervision. Roughly 1,200 individuals who were discharged between the effective date of the executive order and the registration deadline did not have voting rights restored, due largely to their status as noncitizens.

@@

Turnout in the 2018 midterm election is estimated by matching the parole records with the registered voter file. I match individuals in each dataset using first name, middle name, last name, and date of birth. To be considered a ``match,'' records must have the exact same birth date. The first and last names must also be exact matches (conditional on the adjustments discussed below). The middle names must meet one of the following conditions in order to qualify:

\begin{itemize}
\tightlist
\item
  Middle names are identical. If neither set of records includes a middle name, this condition is met.
\item
  A full middle name in one set of records and only a middle initial in the other. The first letter of the full middle name must be the same as the middle initial in the other set of records.
\item
  A middle name or middle initial in one set of records, and a missing middle name in the other set.
\end{itemize}

Thus, ``John Andrew Doe'' and ``John A Doe'' would count as matches. Similarly, ``John Andrew Doe'' and ``John Doe'' would count, while ``John Andrew Doe'' and ``John Anthony Doe'' would not.

There are two types of potential error in this methodology: a false positive will result when a parolee's records matches the record of a voter who is a different individual but shares the same name and date of birth. False negatives will occur when an individual has a different name in the different sets of records, or when the birthdate is incorrectly reported in one of the sets of records

Testing for the presence of false positive matches is fairly straightforward. Meredith and Morse (\protect\hyperlink{ref-Meredith2013}{2013}) offers one way to test their prevalence using placebo matching. I slightly alter the date of birth reported in the parole discharge dataset to create false records. Comparing the number of matches between these ``fake'' discharge records and the voter file with the number of matches between the ``true'' records and the voter file provides an estimate of how frequently false positives occur. Table \ref{tab:change-dobs} shows the results of true matches, as well as when I construct a set of fake records by adding or subtracting 35 days from a parolee's birthdate. This analysis indicates that false positives account for between 0.6 and 0.7 percent of all matches, a share that is likely too small to have any material impact on the overall analysis.

@@

{\centering \includegraphics{../../temp/flowchart}

@@

{\centering \includegraphics{part2_standalone_files/figure-latex/to-16-chart-1}

@@

{\centering \includegraphics{part2_standalone_files/figure-latex/to-18-chart-1}

@@

\input{"../../temp/table3.tex"}
\end{singlespace}

@@

\input{"../../temp/table_whatever2.tex"}
\end{singlespace}

@@

\input{"../../temp/table4.tex"}
\end{singlespace}

@@

\begin{singlespace}
\input{"../../temp/iv_clean.tex"}
\end{singlespace}

@@

{\centering \includegraphics{part2_standalone_files/figure-latex/sensitivity-1}

@@

\begin{singlespace}
\input{"../../temp/iv_clean_race.tex"}
\end{singlespace}

@@

\input{"../../temp/table5.tex"}
\end{singlespace}

@@

\begin{singlespace}
\input{"../../temp/iv_clean_months.tex"}
\end{singlespace}

@@

@@

\leavevmode\hypertarget{ref-bcj_laws}{}%
Justice, Brennan Center for. 2019. ``Criminal Disenfranchisement Laws Across the United States.'' May 30, 2019. \url{https://www.brennancenter.org/our-work/research-reports/criminal-disenfranchisement-laws-across-united-states}.

>>>>

\title{Welcome Home --- Now Vote!}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Voting Rights Restoration and Post-Supervision Participation}

\date{April 08, 2020}

@@

In all but two states (Maine and Vermont), felony disenfranchisement laws mean that American citizens convicted of felony offenses lose the right to vote for at least some period of time. In some states, such as Oregon and Massachusetts, individuals lose that right only for the period in which they are actively incarcerated. Iowa stands alone at the other end of the spectrum, where felony convictions result in lifelong disenfranchisement unless a returned citizen receives an individual pardon from the state's governor (Brennan Center for Justice \protect\hyperlink{ref-bcj_laws}{2019}). This variation in laws arises from language in the Fourteenth Amendment which allows states to revoke individuals' voting rights ``for participation in rebellion, or other crime.'' The definition of ``other crime,'' left so vague in the Constitution, is now generally used by states to disenfranchise citizens for any felony offense. The Supreme Court, in cases such as \emph{Richardson v. Ramirez} (1974), has upheld this practice. Collectively, these laws disenfranchise as many as 4.7 million American citizens. Of these, the majority are no longer incarcerated (Uggen, Larson, and Shannon \protect\hyperlink{ref-sentencing_2016}{2016}).\footnote{The figures reported in Uggen, Larson, and Shannon (\protect\hyperlink{ref-sentencing_2016}{2016}) have been adjusted to reflect the impact of Amendment 4 in Florida.}

@@

Following Executive Order 181, the Department of Corrections and Community Supervision began indicating on their online Parolee Lookup Tool whether a parolee had her voting rights restored. By using the identification number provided from the parolee public records request and this website, I was able to identify individuals who had their voting rights restored.\footnote{Not all parolees listed in the public records request data are included in the lookup tool. Roughly 1 percent of former parolees are not in the online lookup.} There were 5,024 individuals who were discharged from parole before the registration deadline whose rights were restored while still under supervision. Roughly 1,200 individuals who were discharged between the effective date of the executive order and the registration deadline did not have voting rights restored, due largely to their status as noncitizens.

@@

Turnout in the 2018 midterm election is estimated by matching the parole records with the registered voter file. I match individuals in each dataset using first name, middle name, last name, and date of birth. To be considered a ``match,'' records must have the exact same birth date. The first and last names must also be exact matches (conditional on the adjustments discussed below). Middle names must match exactly as well, except for if one record has only a middle initial, which is allowed to match to a full middle name in the other set of records.

I adopt the test developed in Meredith and Morse (\protect\hyperlink{ref-Meredith2013}{2013}) to test the prevalence of false positives. I slightly alter the date of birth reported in the parole discharge dataset to create false records. Comparing the number of matches between these ``fake'' discharge records and the voter file with the number of matches between the ``true'' records and the voter file provides an estimate of how frequently false positives occur. Table \ref{tab:change-dobs} shows the results of true matches, as well as when I construct a set of fake records by adding or subtracting 35 days from a parolee's birthdate. This analysis indicates that false positives account for between 0.6 and 0.7 percent of all matches, a share that is likely too small to have any material impact on the overall analysis.

@@

{\centering \includegraphics{flowchart}

@@

{\centering \includegraphics{to-16-chart-1}

@@

{\centering \includegraphics{to-18-chart-1}

@@

\begin{table}[H] \centering
\fontsize{10}{12}\selectfont
\caption{\label{tab:to-18-logit-short} Individual-Level Logit Models}
\label{}
\begin{tabular}{@{\extracolsep{5pt}}lcc}
\\[-1.8ex]\hline \\[-1.8ex]
\\[-1.8ex] & \multicolumn{2}{c}{Cast Ballot in 2018 Election} \\
\\[-1.8ex] & (1) & (2)\\
\hline \\[-1.8ex]
Days Since Discharged &  & 0.001 \\
&  & (0.003) \\
& & \\
Days Since Discharged\textsuperscript{2} &  & $-$0.00000 \\
&  & (0.00000) \\
& & \\
D(Male) & $-$0.510$^{***}$ & $-$0.511$^{***}$ \\
& (0.183) & (0.183) \\
& & \\
Age (Years) & 0.044$^{***}$ & 0.044$^{***}$ \\
& (0.005) & (0.005) \\
& & \\
Years on Parole & 0.041$^{**}$ & 0.041$^{**}$ \\
& (0.019) & (0.019) \\
& & \\
Constant & $-$6.646$^{***}$ & $-$6.878$^{***}$ \\
& (1.069) & (1.168) \\
& & \\
\hline \\[-1.8ex]
Race / Ethnicity FE & X & X \\
Felony Class FE & X & X \\
\hline \\[-1.8ex]
Observations & 14,155 & 14,155 \\
Log Likelihood & $-$1,365.859 & $-$1,365.740 \\
Akaike Inf. Crit. & 2,761.719 & 2,765.480 \\
\hline \\[-1.8ex]
\multicolumn{3}{l}{\scriptsize{\parbox{.5\linewidth}{\vspace{2pt}$^{***}p<0.01$, $^{**}p<0.05$, $^*p<0.1$. \\Robust standard errors in parentheses.}}}
\end{tabular}
\end{table}

\end{singlespace}

@@

\begin{table}[H]
\fontsize{10}{12}\selectfont

\caption{\label{tab:demo-rd} Demographics of "Control" and "Intent-to-Treat" Groups}
\centering
\begin{tabular}[t]{lcc}
\toprule
Variable & Control & Intend-to-Treat\\
\midrule
Percent Male & 90.3\% & 90.2\%\\
Percent NH-Black & 42.9\% & 41.6\%\\
Percent NH-White & 30.8\% & 31.1\%\\
Percent Latino & 22.6\% & 23.1\%\\
Age (Years)* & 41.5 & 40.4\\
Time Spent on Parole (Years) & 2.2 & 2.1\\
Percent Voted in 2016 & 1.2\% & 1.3\%\\
\bottomrule
\multicolumn{3}{l}{\scriptsize{\parbox{.5\linewidth}{\vspace{2pt}$^*$ Difference is significant at 95 percent confidence level. \\Shows demographics for individuals discharged from parole \\between January 1st, 2017, and October 12th, 2018.}}}
\end{tabular}
\end{table}

\end{singlespace}

@@

\begin{singlespace}
\begin{table}[H] \centering
\fontsize{10}{12}\selectfont
\caption{\label{tab:to-18-logit} Individual-Level Logit Models}
\label{}
\begin{tabular}{@{\extracolsep{5pt}}lccc}
\\[-1.8ex]\hline \\[-1.8ex]
\\[-1.8ex] & \multicolumn{3}{c}{Cast Ballot in 2018 Election} \\
\\[-1.8ex] & (1) & (2) & (3)\\
\hline \\[-1.8ex]
D(Discharged After EO 181) & 0.235$^{**}$ & 0.296$^{***}$ & 0.300$^{***}$ \\
& (0.112) & (0.113) & (0.113) \\
& & & \\
D(Male) &  & $-$0.337$^{**}$ & $-$0.369$^{**}$ \\
&  & (0.158) & (0.159) \\
& & & \\
Age (Years) &  & 0.051$^{***}$ & 0.045$^{***}$ \\
&  & (0.004) & (0.004) \\
& & & \\
Years on Parole &  &  & 0.037$^{**}$ \\
&  &  & (0.016) \\
& & & \\
Constant & $-$3.839$^{***}$ & $-$7.278$^{***}$ & $-$7.223$^{***}$ \\
& (0.059) & (1.050) & (1.054) \\
& & & \\
\hline \\[-1.8ex]
Race / Ethnicity FE &  & X & X \\
Felony Class FE &  &  & X \\
\hline \\[-1.8ex]
Observations & 18,423 & 18,423 & 18,423 \\
Log Likelihood & $-$1,967.190 & $-$1,872.755 & $-$1,859.151 \\
Akaike Inf. Crit. & 3,938.380 & 3,765.509 & 3,750.302 \\
\hline \\[-1.8ex]
\multicolumn{4}{l}{\scriptsize{\parbox{.5\linewidth}{\vspace{2pt}$^{***}p<0.01$, $^{**}p<0.05$, $^*p<0.1$. \\Robust standard errors in parentheses.}}}
\end{tabular}
\end{table}

\end{singlespace}

@@

\begin{singlespace}
\begin{table}[H]
\caption{\label{tab:iv-models-chunk}\label{tab:iv-models} Rights Restoration and Turnout}
\fontsize{10}{12}\selectfont
\centering

\begin{tabular}{lccccc}
\\[-1.8ex]\hline
& \multicolumn{5}{c}{Cast Ballot in 2018 Election} \\
& \multicolumn{2}{c}{2SLS} & \multicolumn{1}{c}{2S Probit} &   \multicolumn{2}{c}{Bivariate Probit}\\
& & & \multicolumn{1}{c}{(Marg. Effects)} &   \multicolumn{2}{c}{(Marg. Effects)}\\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-6}
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5)\\
\hline
D(Rights Restored) & 0.0075** & 0.0096** & 0.0169*** & 0.0063** & 0.0084*** \\
 & (0.0038) & (0.0038) & (0.0036) & (0.0030) & (0.0031) \\
D(Male) &  & -0.0085** & -0.0079** &  & -0.0081** \\
 &  & (0.0042) & (0.0035) &  & (0.0035) \\
Age (Years) &  & 0.0011*** & 0.0010*** &  & 0.0010*** \\
 &  & (0.0001) & (0.0001) &  & (0.0001) \\
Years on Parole &  & 0.0015** & 0.0011** &  & 0.0011** \\
 &  & (0.0006) & (0.0004) &  & (0.0004) \\
Constant & 0.0210*** & -0.0416*** &  &  &  \\
 & (0.0012) & (0.0090) &  &  &  \\
\hline
Race / Ethnicity FE &  & X & X &  & X \\
Felony Class FE &  & X & X &  & X \\
\hline
Observations & 18,423 & 18,423 & 18,423 & 18,423 & 18,423 \\
Adjusted R$^2$ & 0.0007 & 0.0134 &  &  &  \\
Wald $\chi^2$ &  &  & 210.2 & 1168 & 1571 \\
 $\rho$ &  &  &  & 0.138 & 0.0803 \\
\hline
\multicolumn{3}{l}{\scriptsize{\parbox{.5\linewidth}{\vspace{2pt}$^{***}p<0.01$, $^{**}p<0.05$, $^*p<0.1$. \\
Robust standard errors in parentheses. \\
Instrument is dummy indicating whether \\
individual discharged after EO 181 went into effect. \\
First-stage equations include covariates in Models 2 -- 3. \\
Models 3 -- 5 present marginal effects, not model coefficients.}}}
\end{tabular}
\end{table}

\end{singlespace}

@@

{\centering \includegraphics{sensitivity-1}

@@

\begin{singlespace}
\begin{table}[H]
\caption{\label{tab:iv-models-r-chunk}\label{tab:iv-models-r} Rights Restoration and Turnout}
\fontsize{10}{12}\selectfont
\centering

\begin{tabular}{lcccccc}
\\[-1.8ex]\hline
& \multicolumn{6}{c}{Cast Ballot in 2018 Election} \\
& \multicolumn{3}{c}{2SLS} &  \multicolumn{3}{c}{Bivariate Probit}\\
& & & &   \multicolumn{3}{c}{(Marg. Effects)}\\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
\\[-1.8ex] & White & Non-White & Black& White & Non-White & Black\\
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\
\hline
D(Rights Restored) & 0.0182*** & 0.0045 & 0.0032 & 0.0176*** & 0.0039 & 0.0033 \\
 & (0.0067) & (0.0045) & (0.0057) & (0.0067) & (0.0034) & (0.0046) \\
D(Male) & -0.0020 & -0.0165** & -0.0202** & -0.0009 & -0.0141*** & -0.0174*** \\
 & (0.0052) & (0.0067) & (0.0091) & (0.0054) & (0.0045) & (0.0061) \\
Age (Years) & 0.0016*** & 0.0009*** & 0.0010*** & 0.0013*** & 0.0008*** & 0.0010*** \\
 & (0.0002) & (0.0001) & (0.0002) & (0.0002) & (0.0001) & (0.0002) \\
Years on Parole & 0.0037** & 0.0008 & 0.0024** & 0.0023** & 0.0006 & 0.0018** \\
 & (0.0018) & (0.0007) & (0.0011) & (0.0011) & (0.0005) & (0.0007) \\
Constant & -0.0498*** & -0.0100 & -0.0143 &  &  &  \\
 & (0.0113) & (0.0092) & (0.0127) &  &  &  \\
\hline
Felony Class FE & X & X & X & X & X & X \\
\hline
Observations & 5,691 & 12,732 & 7,843 & 5,691 & 12,732 & 7,843 \\
Adjusted R$^2$ & 0.0211 & 0.0095 & 0.0140 &  &  &  \\
Wald $\chi^2$ &  &  &  & 414.2 & 1207 & 984.2 \\
 $\rho$ &  &  &  & -0.181 & 0.255 & 0.291 \\
\hline
\multicolumn{3}{l}{\scriptsize{\parbox{.5\linewidth}{\vspace{2pt}$^{***}p<0.01$, $^{**}p<0.05$, $^*p<0.1$. \\
Robust standard errors in parentheses. \\
Instrument is dummy indicating whether \\
individual discharged after EO 181 went into effect. \\
First-stage equations include covariates in all models. \\
Models 4 -- 6 present marginal effects, not model coefficients.}}}
\end{tabular}
\end{table}

\end{singlespace}

@@

\begin{singlespace}
\begin{table}[H] \centering
\fontsize{10}{12}\selectfont
\caption{\label{tab:black-to} Turnout Rate Among Former Parolees}
\label{}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc}
\\[-1.8ex]\hline \\[-1.8ex]
\\[-1.8ex] & \multicolumn{6}{c}{Cast Ballot in 2018 Election} \\
& \multicolumn{2}{c}{Discharged Prior to EO} & \multicolumn{2}{c}{ITT Group} & \multicolumn{2}{c}{Treatment Group} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}  \cmidrule(l{3pt}r{3pt}){6-7}
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\
\hline \\[-1.8ex]
D(Black) & 0.417$^{***}$ & 0.285$^{**}$ & 0.039 & $-$0.161 & 0.084 & $-$0.039 \\
& (0.121) & (0.141) & (0.197) & (0.215) & (0.212) & (0.236) \\
& & & & & & \\
D(Male) & $-$0.563$^{***}$ & $-$0.486$^{**}$ & $-$0.053 & $-$0.119 & 0.053 & $-$0.019 \\
& (0.178) & (0.195) & (0.327) & (0.332) & (0.364) & (0.369) \\
& & & & & & \\
Age (Years) & 0.045$^{***}$ & 0.045$^{***}$ & 0.050$^{***}$ & 0.052$^{***}$ & 0.048$^{***}$ & 0.051$^{***}$ \\
& (0.005) & (0.005) & (0.007) & (0.008) & (0.008) & (0.009) \\
& & & & & & \\
Years on Parole & 0.033$^{*}$ & 0.049$^{**}$ & 0.017 & 0.075 & 0.133$^{**}$ & 0.135$^{**}$ \\
& (0.019) & (0.023) & (0.033) & (0.046) & (0.054) & (0.057) \\
& & & & & & \\
Constant & $-$5.825$^{***}$ & $-$5.862$^{***}$ & $-$6.125$^{***}$ & $-$5.991$^{***}$ & $-$6.182$^{***}$ & $-$6.075$^{***}$ \\
& (0.299) & (0.321) & (0.486) & (0.530) & (0.548) & (0.601) \\
& & & & & & \\
\hline \\[-1.8ex]
Observations & 14,155 & 10,963 & 4,268 & 3,280 & 3,093 & 2,514 \\
Log Likelihood & $-$1,371.825 & $-$1,133.731 & $-$492.408 & $-$402.919 & $-$402.966 & $-$341.008 \\
Akaike Inf. Crit. & 2,763.649 & 2,287.462 & 1,004.817 & 825.838 & 825.932 & 702.015 \\
\hline \\[-1.8ex]
\multicolumn{7}{l}{\scriptsize{\parbox{.5\linewidth}{\vspace{2pt}$^{***}p<0.01$, $^{**}p<0.05$, $^*p<0.1$. \\Robust standard errors in parentheses. \\Latino individuals excluded from Models 2, 4, and 6.}}}
\end{tabular}
\end{table}

\end{singlespace}

@@

\begin{singlespace}
\begin{table}[H]
\caption{\label{tab:iv-models-chunk-time}\label{tab:iv-models-time} Rights Restoration and Turnout}
\fontsize{10}{12}\selectfont
\centering

\begin{tabular}{lcc}
\\[-1.8ex]\hline
& \multicolumn{2}{c}{Cast Ballot in 2018 Election} \\
& \multicolumn{1}{c}{2SLS} & \multicolumn{1}{c}{2S Probit}\\
& &  \multicolumn{1}{c}{(Marg. Effects)}\\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3}
\\[-1.8ex] & (1) & (2) \\
\hline
Months Restored & 0.0029** & 0.0050*** \\
 & (0.0011) & (0.0010) \\
D(Male) & -0.0084** & -0.0080** \\
 & (0.0042) & (0.0035) \\
Age (Years) & 0.0011*** & 0.0010*** \\
 & (0.0001) & (0.0001) \\
Years on Parole & 0.0015** & 0.0011** \\
 & (0.0006) & (0.0004) \\
Constant & -0.0418*** &  \\
 & (0.0090) &  \\
\hline
Race / Ethnicity FE & X & X \\
Felony Class FE & X & X \\
\hline
Observations & 18,423 & 18,423 \\
Adjusted R$^2$ & 0.0134 &  \\
 Wald $\chi^2$ &  & 210.9 \\
\hline
\multicolumn{3}{l}{\scriptsize{\parbox{.5\linewidth}{\vspace{2pt}$^{***}p<0.01$, $^{**}p<0.05$, $^*p<0.1$. \\
Robust standard errors in parentheses. \\
Instrument is dummy indicating whether \\
individual discharged after EO 181 went into effect. \\
First-stage equations include covariates in both models. \\
Model 2 presents marginal effects, not model coefficients.}}}
\end{tabular}
\end{table}

\end{singlespace}

@@

\leavevmode\hypertarget{ref-bcj_laws}{}%
Brennan Center for Justice. 2019. ``Criminal Disenfranchisement Laws Across the United States.'' May 30, 2019. \url{https://www.brennancenter.org/our-work/research-reports/criminal-disenfranchisement-laws-across-united-states}.

@@

### 2020-07-06 markdown/part2/part2_standalone.Rmd
commit july 6

## Matching {-}
Turnout in the 2018 midterm election is estimated by matching the parole records with the registered voter file. I match individuals in each dataset using first name, middle name, last name, and date of birth. To be considered a "match," records must have the exact same birth date. The first and last names must also be exact matches (conditional on the adjustments discussed below). The middle names must meet one of the following conditions in order to qualify:

* Middle names are identical. If neither set of records includes a middle name, this condition is met.
* A full middle name in one set of records and only a middle initial in the other. The first letter of the full middle name must be the same as the middle initial in the other set of records.
* A middle name or middle initial in one set of records, and a missing middle name in the other set.

Thus, "John Andrew Doe" and "John A Doe" would count as matches. Similarly, "John Andrew Doe" and "John Doe" would count, while "John Andrew Doe" and "John Anthony Doe" would not.

There are two types of potential error in this methodology: a false positive will result when a parolee's records matches the record of a voter who is a different individual but shares the same name and date of birth. False negatives will occur when an individual has a different name in the different sets of records, or when the birthdate is incorrectly reported in one of the sets of records

Testing for the presence of false positive matches is fairly straightforward. @Meredith2013 offers one way to test their prevalence using placebo matching. I slightly alter the date of birth reported in the parole discharge dataset to create false records. Comparing the number of matches between these "fake" discharge records and the voter file with the number of matches between the "true" records and the voter file provides an estimate of how frequently false positives occur. Table \ref{tab:change-dobs} shows the results of true matches, as well as when I construct a set of fake records by adding or subtracting 35 days from a parolee's birthdate. This analysis indicates that false positives account for between 0.6 and 0.7 percent of all matches, a share that is likely too small to have any material impact on the overall analysis.
\begin{singlespace}
```{r shift-dobs-chunk, echo = F}
less_35 <- scales::comma(readRDS("./temp/m35_2.rds"))
true <- scales::comma(nrow(readRDS("./temp/din_nys_parolees.rds")))
plus_35 <- scales::comma(readRDS("./temp/p35_2.rds"))

>>>>

## Matching {-}
Turnout in the 2018 midterm election is estimated by matching the parole records with the registered voter file. I match individuals in each dataset using first name, middle name, last name, and date of birth. To be considered a "match," records must have the exact same birth date. The first and last names must also be exact matches (conditional on the adjustments discussed below). Middle names must match exactly as well, except for if one record has only a middle initial, which is allowed to match to a full middle name in the other set of records.

I adopt the test developed in @Meredith2013 to test the prevalence of false positives. I slightly alter the date of birth reported in the parole discharge dataset to create false records. Comparing the number of matches between these "fake" discharge records and the voter file with the number of matches between the "true" records and the voter file provides an estimate of how frequently false positives occur. Table \ref{tab:change-dobs} shows the results of true matches, as well as when I construct a set of fake records by adding or subtracting 35 days from a parolee's birthdate. This analysis indicates that false positives account for between 0.6 and 0.7 percent of all matches, a share that is likely too small to have any material impact on the overall analysis.
\begin{singlespace}
```{r shift-dobs-chunk, echo = F}
less_35 <- scales::comma(readRDS("./temp/m35_2.rds"))
true <- scales::comma(nrow(readRDS("./temp/din_nys_parolees.rds")))
plus_35 <- scales::comma(readRDS("./temp/p35_2.rds"))
